---
title: "Open Scholarship @ Penn State"
subtitle: "Join us!"
author: "Ana Enriquez, Rick Gilmore, Frank Hillary, Nicole Lazar, Alaina Pearce, & Briana Wham"
format: 
  revealjs:
    # footer: "Open Scholarship Blitz"
    slide-number: true
    fig-align: center
    logo: https://brand.psu.edu/images/backgrounds/penn-state-shield.jpg
    css: include/css/styles.css
knitr:
  opts_chunk:
    fig.path: include/fig/
---

---

::: {layout="[[1,1], [1,1]]"}
![Open Science [Bootcamp 2023](https://penn-state-open-science.github.io/bootcamp-2023/)](https://penn-state-open-science.github.io/bootcamp-2023/include/img/make-word-cloud-1.png){width="60%" align="center"}

![Interest & knowledge [surveys](https://penn-state-open-science.github.io/survey-fall-2022/data-visualization.html)](https://penn-state-open-science.github.io/survey-fall-2022/include/img/fig-experience-w-open-science-1.png){width="60%" .lightbox}

![Data management [workshop 2024](https://penn-state-open-science.github.io/data-mgmt-2024/)](https://teacherhead.com/wp-content/uploads/2017/02/9464b325-d2f4-4604-8258-82093bf93af6.jpg){width="60%"}

![[Speaker](https://penn-state-open-science.github.io/bootcamp-2023/presentation-topics.html#keynote) series](include/img/errington-bootcamp-2023.jpg){width="60%"}
:::

---

:::: {.columns}
::: {.column width="25%"}

Ana Enriquez</br>
University Libraries</br>
aee32@psu.edu</br></br>

Rick Gilmore</br>
Psychology</br>
rog1@psu.edu</br></br>

Frank Hillary</br>
Psychology</br>
fgh3@psu.edu

:::
::: {.column width="50%"}
```{r}
#| label: fig-qr-code
#| fig-cap: "https://penn-state-open-science.github.io/outreach-talk"
code <- qrcode::qr_code("https://penn-state-open-science.github.io/outreach-talk")
plot(code)
```

```{r}
#| label: fig-qr-code-gh
#| fig-cap: "https://github.com/penn-state-open-science"
code <- qrcode::qr_code("https://github.com/penn-state-open-science")
plot(code)
```
:::
::: {.column width="25%"}

Nicole Lazar</br>
Statistics</br>
nfl5182@psu.edu</br></br>

Alaina Pearce</br>
Nutrition</br>
azp271@psu.edu</br></br>

Briana Wham</br>
bde125@psu.edu

:::
::::
